Ground state energy of quantum dots using the coupled cluster method

### 2018-06-05 project_2/article/article.tex
Begin implementation section in report

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Tikz add-on
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
% Several figures in the same figure
\usepackage{subfig}
% Appendix
\usepackage[toc, page]{appendix}
\usepackage{simpler-wick}
% Code listings
\usepackage{listings, lstautogobble}
% Colors
\usepackage{xcolor}

@@

% Bash language specifier
\lstnewenvironment{bash}
{\lstset{
    basicstyle=\small\ttfamily, language=bash, keywordstyle=\color{blue},
    backgroundcolor=\color{light-gray}, showstringspaces=false,
    frame=single, autogobble=true, morekeywords={make, git}}}
{}

@@

   \section{Implmentation}
        We have costructed a flexible framework for making performing CCD computations,
        consisting of package for python that is easy to install globally on any 
        computer.

        \subsection{Installation}
        The software is easy to install by first cloning the GitHub reopsitory,
        \begin{bash}
            git clone git@github.com:Schoyen/FYS4411.git
        \end{bash}
        Then all you need to do is change directory to the project code folder
        where a \lstinline{MakeFile} is included so you only need to build and
        install,
        \begin{bash}
            cd FYS4411/project_2/coupled-cluster
            make build
            make install
        \end{bash}

@@

>>>>

% It's nice to be able to write your own name
\usepackage[T1]{fontenc}
% Automatic clickable links
\usepackage{hyperref}
% SI-units
\usepackage{siunitx}
% Enhanced math formatting
\usepackage{amsmath}
% Extended math symbols
\usepackage{amssymb}
% Include proof environment
\usepackage{amsthm}
\usepackage{enumerate}
% Import the tensor package for tensors
\usepackage{tensor}
% Include dod and dpd fracs
\usepackage{commath}
% Include font for the identity operator
\usepackage{dsfont}
% Include Tikz
\usepackage{tikz}
% Tikz add-on
\usetikzlibrary{shapes,arrows}
\usetikzlibrary{positioning}
% Several figures in the same figure
\usepackage{subfig}
% Appendix
\usepackage[toc, page]{appendix}
\usepackage{simpler-wick}
% Code listings
\usepackage{listings, lstautogobble}
\usepackage{minted}
% Colors
\usepackage{xcolor}
% Directory tree package
\usepackage{dirtree, varwidth}

@@

% Bash language specifier
\lstnewenvironment{bash}
{\lstset{
    basicstyle=\small\ttfamily, language=bash, keywordstyle=\color{blue},
    backgroundcolor=\color{light-gray}, showstringspaces=false,
    frame=single, autogobble=true, morekeywords={make, git},
    alsoletter={.}}}
{}

@@

   \section{Implmentation}
        We have costructed a flexible framework for making performing CCD computations,
        consisting of package for \lstinline{python} that is easy to install globally on any 
        computer.

        \subsection{Installation}
        The software is easy to install by first cloning the GitHub reopsitory,
        \begin{bash}
            git clone git@github.com:Schoyen/FYS4411.git
        \end{bash}
        Then all you need to do is change directory to the project code folder
        where a \lstinline{MakeFile} is included so you only need to build and
        install,
        \begin{bash}
            cd FYS4411/project_2/coupled-cluster
            make build
            make install
        \end{bash}
        Now everything should be able to run from anywhere on your computer.
        To ensure that all requirements of the program are satified you can
        install with \lstinline{make installr} instead.

        \subsection{Program Structure}
            There are three main subsetions within our program structure,
            given in the directory tree below.

            %% NONE OF THIS WORKED AS INTENDED.
            %\begin{figure}
            %\centering
            %\framebox[0.5\textwidth]{%
            %\begin{minipage}{0.49\textwidth}
            %\begin{center}
            %\begin{varwidth}{0.49\textwidth}
            %\dirtree{%
            %.1 coupled\_cluster.
            %    .2 matrix\_elements.
            %        .3 generate\_matrices. 
            %        .3 index\_map.
            %    .2 hartree\_fock.
            %        .3 scf\_rhf.
            %        .3 basis\_transformation.
            %    .2 schemes.
            %        .3 ccd.
            %        .3 ccd\_sparse.
            %        .3 ccd\_optimized.
            %}
            %\end{varwidth}
            %\end{center}
            %\end{minipage}  
            %}  
            %\end{figure}

            \vspace{10pt}
            \dirtree{%
            .1 coupled\_cluster.
                .2 matrix\_elements.
                    .3 generate\_matrices. 
                    .3 index\_map.
                .2 hartree\_fock.
                    .3 scf\_rhf.
                    .3 basis\_transformation.
                .2 schemes.
                    .3 ccd.
                    .3 ccd\_sparse.
                    .3 ccd\_optimized.
            }
            \vspace{10pt}

            The first subsection, \mintinline{python}{matrix_elemtents},
            contains methods for computing matrix elements in harmonic oscillator
            basis from an analytical expression\cite{anisimovas1998energy}. 
            Computing the matrix elements is a very intensive task, and the central
            functions are therefore implemented in C++ with a Cython interface to
            enable use in Python.

            The \mintinline{python}{hartree_fock} subsection contains methods for changing
            from harmonic oscillator basis to Hartree-Fock basis as well as an 
            implementation of the self-consistent-field algorithm to make this
            transaction possible.

            The \mintinline{python}{schemes} subsection is arguably the most important part
            of this project. The subsection has three different classes that perform
            the exact same computations, but in different and increasingly intelligent
            ways. First, \mintinline{python}{CoupledClusterDoubles} is the most 
            straightforward and naïve way to solve the CCD amplitude equations.
            Second, because an overbearing amount of the elements in the operator matrices
            in this problem are zero, we have implemented a sparse matrix CDD solver in
            \mintinline{python}{CoupledClusterDoublesSparse}. Third,
            \mintinline{python}{CoupledClusterDoublesOptimized} takes advantage of 
            sparse matrices as well, but is also parallellized and optimized with
            memory use and number of floating point operations in mind.

@@

\section{Example Script}

    \vspace{10pt}
    \begin{widetext}
    \inputminted[]{python}{../scripts/comparison.py}
    \end{widetext}
